FourierTools.jl - Working with Fourier Space

### 2022-05-05 paper/paper.tex
Update paper.tex
Replace some expressions for pgfplots [skip ci]
Fix missing brackets in paper [skip ci]

\section{Introduction}
The fast Fourier transform (FFT) is a popular algorithm because it can evaluate the Discrete Fourier Transform (DFT) 
\begin{equation}
    X_k = \sum_{n=0}^{N-1} x_n \exp\left(-i2 \pi \frac{kn}{N} \right)
    \label{eq:dft}
\end{equation}
and the Inverse Discrete Fourier Transform (IDFT)
\begin{equation}
    x_n = \frac1{N}\sum_{n=0}^{N-1} X_k \exp\left(i2 \pi \frac{kn}{N} \right)
    \label{eq:idft}
\end{equation}
in $\mathcal{O}(N \log N)$ operations, whereas the straightforward
evaluation takes $\mathcal{O}(N^2)$ operations.
The DFT transforms the signal to a different basis, the Fourier space which
has wide applications in signal processing.
In Julia \cite{bezanson2017julia} \verb|FFTW.jl| offers a convenient interface to
the \verb|FFTW| library \cite{FFTW05} which is among the fastest FFT libraries.
The interpretation of a signal in Fourier space is versatile and many operations can
be done using FFT operations. 
In this work, we present several operations which can be calculated quickly 
due to the good performance of FFTs.
Additionally, we also stick to a certain boundary handling in all algorithms.
All algorithms and examples are implemented using the Julia package \verb|FourierTools.jl|\footnote{The full source is available on GitHub: \url{https://github.com/bionanoimaging/FourierTools.jl/}}.

@@

    As seen from \autoref{eq:DFS}, the maximum frequency of a signal described with the DFS is $-\lfloor N/2 \rfloor / L$ (the border of the summation interval of $k = -\lfloor N/2 \rfloor$)\footnote{You might wonder why the maximum frequency in \autoref{eq:DFS2} would be at $k=N-1$. However, this frequency is not Nyquist sampled\footnote{According to the Whittaker–Nyquist–Shannon 
        theorem \cite{whittaker_e_t_1915_1428702}, \cite{Shannon1949}.} and leads to aliasing which results that those frequencies appear at lower frequencies.}. 
    For a signal (over the range $[0, L)$) with 7 elements, the frequencies in the Fourier series would be
    \begin{equation}
        f_{\{k\}} = \left[-\frac{3}{7 L} , -\frac{2}{7 L},  -\frac{1}{7L}, \frac{0}{7L}, \frac{1}{7L}, \frac{2}{7L}, \frac{3}{7L} \right]
        \label{eq:7elems}
    \end{equation}
    and for one with 6 elements
    \begin{equation}
       f_{\{k\}} = \left[-\frac{4}{8 L} ,-\frac{3}{8 L} ,-\frac{2}{8 L} ,-\frac{1}{8 L} ,\frac{0}{8 L} ,\frac{1}{8 L} ,\frac{2}{8 L} ,\frac{3}{8 L} \right].
       \label{eq:6elems}
    \end{equation}
    The highest frequency $-\frac{4}{8 L}$ in \autoref{eq:6elems} does not fulfill Nyquist sampling and thus 
    cannot be interpreted uniquely. As drawn in \autoref{fig:nyquist_sample}, comparing the solid green, red and blue curves, there are infinitely many periodic functions of one and the same coarsest frequency
     (varying in phase and amplitude) exhibiting same sampled values.
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \begin{axis}[xmin=-0.5, xmax=7, ymax=1.2, ymin=-1.2, width=8cm, height=5cm,
                xtick = {0, 3.1415, 2 * 3.1414}, xticklabels={0, $L/2$, $L$}]
                    \addplot[sharp plot, domain=-1:9, color=green, samples=400] {0.2 * cos(deg(x)};
                    \addplot[sharp plot, domain=-1:9, color=blue, samples=100] {0.5 * cos(deg(x) - 66.42};
                    \addplot[sharp plot, domain=-1:9, color=red, samples=100] {1 * cos(deg(x) - 78.46};
                    \addplot[sharp plot, domain=-1:9, color=orange, samples=100] {0.2*cos(deg( 3 *x))};
                    \draw[] (axis cs:-1, 0) -- (axis cs:8, 0);
                    \draw[dashed] (axis cs:0, -2) -- (axis cs:0, 2);
                    \draw[dashed] (axis cs:3.1415, -2) -- (axis cs:3.1415, 2);
                    \draw[dashed] (axis cs:3.1415*2, -2) -- (axis cs:3.1415*2, 2);

                   \draw (0,0.2) node[cross, thick] { };
                    \draw (3.1415,-0.2) node[cross, thick] { };
                     \draw (2 * 3.1415,0.2) node[cross, thick] { };

>>>>

\section{Introduction}
The fast Fourier transform (FFT) is a popular algorithm because it can evaluate the Discrete Fourier Transform (DFT) 
\begin{equation}
    X_k = \sum_{n=0}^{N-1} x_n \exp\left(-i2 \pi \frac{kn}{N} \right)
    \label{eq:dft}
\end{equation}
and the Inverse Discrete Fourier Transform (IDFT)
\begin{equation}
    x_n = \frac1{N}\sum_{k=0}^{N-1} X_k \exp\left(i2 \pi \frac{kn}{N} \right)
    \label{eq:idft}
\end{equation}
in $\mathcal{O}(N \log N)$ operations, whereas the straightforward
evaluation takes $\mathcal{O}(N^2)$ operations.
The DFT transforms the signal to a different basis, the Fourier space which
has wide applications in signal processing.
In Julia \cite{bezanson2017julia} \verb|FFTW.jl| offers a convenient interface to
the \verb|FFTW| library \cite{FFTW05} which is among the fastest FFT libraries.
The interpretation of a signal in Fourier space is versatile and many operations can
be done using FFT operations. 
In this work, we present several operations which can be calculated quickly 
due to the good performance of FFTs.
Additionally, we also stick to a certain boundary handling in all algorithms.
All algorithms and examples are implemented using the Julia package \verb|FourierTools.jl|\footnote{The full source is available on GitHub: \url{https://github.com/bionanoimaging/FourierTools.jl/}}.

@@

    As seen from \autoref{eq:DFS}, the maximum frequency of a signal described with the DFS is $-\lfloor N/2 \rfloor / L$ (the border of the summation interval of $k = -\lfloor N/2 \rfloor$)\footnote{You might wonder why the maximum frequency in \autoref{eq:DFS2} would be at $k=N-1$. However, this frequency is not Nyquist sampled\footnote{According to the Whittaker–Nyquist–Shannon 
        theorem \cite{whittaker_e_t_1915_1428702}, \cite{Shannon1949}.} and leads to aliasing which results that those frequencies appear at lower frequencies.}. 
    For a signal (over the range $[0, L)$) with 7 elements, the frequencies in the Fourier series would be
    \begin{equation}
        f_{\{k\}} = \left[-\frac{3}{7 L} , -\frac{2}{7 L},  -\frac{1}{7L}, \frac{0}{7L}, \frac{1}{7L}, \frac{2}{7L}, \frac{3}{7L} \right]
        \label{eq:7elems}
    \end{equation}
    and for one with 6 elements
    \begin{equation}
       f_{\{k\}} = \left[-\frac{4}{8 L} ,-\frac{3}{8 L} ,-\frac{2}{8 L} ,-\frac{1}{8 L} ,\frac{0}{8 L} ,\frac{1}{8 L} ,\frac{2}{8 L} ,\frac{3}{8 L} \right].
       \label{eq:6elems}
    \end{equation}
    The highest frequency $-\frac{4}{8 L}$ in \autoref{eq:6elems} does not fulfill Nyquist sampling and thus 
    cannot be interpreted uniquely. As drawn in \autoref{fig:nyquist_sample}, comparing the solid green, red and blue curves, there are infinitely many periodic functions of one and the same coarsest frequency
     (varying in phase and amplitude) exhibiting same sampled values.
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \begin{axis}[xmin=-0.5, xmax=7, ymax=1.2, ymin=-1.2, width=8cm, height=5cm,
                xtick = {0, 3.1415, 6.283}, xticklabels={0, $L/2$, $L$}]
                    \addplot[sharp plot, domain=-1:9, color=green, samples=400] {0.2 * cos(deg(x))};
                    \addplot[sharp plot, domain=-1:9, color=blue, samples=100] {0.5 * cos(deg(x) - 66.42)};
                    \addplot[sharp plot, domain=-1:9, color=red, samples=100] {1 * cos(deg(x) - 78.46)};
                    \addplot[sharp plot, domain=-1:9, color=orange, samples=100] {0.2*cos(deg( 3 *x))};
                    \draw[] (axis cs:-1, 0) -- (axis cs:8, 0);
                    \draw[dashed] (axis cs:0, -2) -- (axis cs:0, 2);
                    \draw[dashed] (axis cs:3.1415, -2) -- (axis cs:3.1415, 2);
                    \draw[dashed] (axis cs:6.283, -2) -- (axis cs:6.283, 2);

                   \draw (0,0.2) node[cross, thick] { };
                    \draw (3.1415,-0.2) node[cross, thick] { };
                     \draw (6.283,0.2) node[cross, thick] { };
